A linear inside-outside algorithm for correcting sequencing errors in structured RNA sequences

### 2012-10-08 Recomb/conclusion_RECOMB.tex
fixed typo

In this article we presented a new and efficient way of exploring the mutational landscape of an RNA under structural constraints,
and apply our techniques to identify and fix sequencing errors. In adddition, we introduce a new
scoring scheme combining the nearest-neighbour energy model to new isostericity matrices in order to account for geometrical
discrepancies occurring during base pair replacements.
The algorithm runs in  $\Theta(n\cdot(|\Omega|+m^2))$ time and $\Theta(n\cdot(|\Omega|+m))$ memory, where $n$ is the length of the RNA,
$m$ the number of mutations and $\Omega$ the size of the multiple sequence alignment.

>>>>

In this article we presented a new and efficient way of exploring the mutational landscape of an RNA under structural constraints,
and apply our techniques to identify and fix sequencing errors. In addition, we introduce a new
scoring scheme combining the nearest-neighbour energy model to new isostericity matrices in order to account for geometrical
discrepancies occurring during base pair replacements.
The algorithm runs in  $\Theta(n\cdot(|\Omega|+m^2))$ time and $\Theta(n\cdot(|\Omega|+m))$ memory, where $n$ is the length of the RNA,
$m$ the number of mutations and $\Omega$ the size of the multiple sequence alignment.
